---
title: "Lung Health Checks, 5-Year Model"
author: "NHS Transformation Unit"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    toc_collapsed: true
    css: ../config/nhs_tu_theme.css
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

source("../model/lhc_model.R")
source("../visualisation/visualisations_run.R")

```

```{r logo, echo = FALSE}

htmltools::img(src = knitr::image_uri(paste0(here(), "/images/TU_logo_large.png")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:5%; padding:10px;',
               width = "180px",
               heigth = "180px")

```

## Introduction {.tabset .tabset-fade}
***

### Background to the Model


<br/>

### Assumptions

<br/>


### Pathway

<br/>

## Year 1 Projections {.tabset .tabset-fade}
***

This section provides an overview of the projected activity and outcomes at each point of the pathway during the first year of the model. Within each tab there is a summary of the activity projected from the `r trials` model runs undertaken.


### Population uptake {.tabset .tabset-fade}
In the first stage of the model patients are randomised to be invited for a Lung Health Check. This is based on the uptake rates set within the model assumptions.

#### Summary

<br/>

#### Distribution of Uptake Population
The chart below is a histogram showing the distribution of the number of patients invited across each of the `r trials` model runs.

```{r y1_uptake_hist, out.width='100%'}

y1_uptake_hist

```

<br/>

### Lung Health Checks
Placeholder.

### CT Scans
Placeholder.

### Initial Treatments
Placeholder.

### 3M Treatments
Placeholder.

### 12M Treatments
Placeholder.

### 24M Treatments
Placeholder.


## Year 2 Projections {.tabset .tabset-fade}
***

This section provides an overview of the projected activity and outcomes at each point of the pathway during the second year of the model. Within each tab there is a summary of the activity projected from the `r trials` model runs undertaken.


### Population uptake {.tabset .tabset-fade}
In the first stage of the model patients are randomised to be invited for a Lung Health Check. This is based on the uptake rates set within the model assumptions.

#### Summary

<br/>

#### Distribution of Uptake Population
The chart below is a histogram showing the distribution of the number of patients invited across each of the `r trials` model runs.

```{r y2_uptake_hist, out.width='100%'}

y2_uptake_hist

```

<br/>


### Population uptake
Placeholder.

### Lung Health Checks
Placeholder.

### CT Scans
Placeholder.

### Initial Treatments
Placeholder.

### 3M Treatments
Placeholder.

### 12M Treatments
Placeholder.

### 24M Treatments
Placeholder.


## Year 3 Projections {.tabset .tabset-fade}
***

This section provides an overview of the projected activity and outcomes at each point of the pathway during the third year of the model. Within each tab there is a summary of the activity projected from the `r trials` model runs undertaken.


### Population uptake {.tabset .tabset-fade}
In the first stage of the model patients are randomised to be invited for a Lung Health Check. This is based on the uptake rates set within the model assumptions.

#### Summary

<br/>

#### Distribution of Uptake Population
The chart below is a histogram showing the distribution of the number of patients invited across each of the `r trials` model runs.

```{r y3_uptake_hist, out.width='100%'}

y3_uptake_hist

```

<br/>


### Population uptake
Placeholder.

### Lung Health Checks
Placeholder.

### CT Scans
Placeholder.

### Initial Treatments
Placeholder.

### 3M Treatments
Placeholder.

### 12M Treatments
Placeholder.

### 24M Treatments
Placeholder.


## Year 4 Projections {.tabset .tabset-fade}
***

This section provides an overview of the projected activity and outcomes at each point of the pathway during the fourth year of the model. Within each tab there is a summary of the activity projected from the `r trials` model runs undertaken.


### Population uptake {.tabset .tabset-fade}
In the first stage of the model patients are randomised to be invited for a Lung Health Check. This is based on the uptake rates set within the model assumptions.

#### Summary

<br/>

#### Distribution of Uptake Population
The chart below is a histogram showing the distribution of the number of patients invited across each of the `r trials` model runs.

```{r y4_uptake_hist, out.width='100%'}

y4_uptake_hist

```

<br/>


### Population uptake
Placeholder.

### Lung Health Checks
Placeholder.

### CT Scans
Placeholder.

### Initial Treatments
Placeholder.

### 3M Treatments
Placeholder.

### 12M Treatments
Placeholder.

### 24M Treatments
Placeholder.


## Year 5 Projections {.tabset .tabset-fade}
***

This section provides an overview of the projected activity and outcomes at each point of the pathway during the final year of the model. Within each tab there is a summary of the activity projected from the `r trials` model runs undertaken.


### Population uptake {.tabset .tabset-fade}
In the first stage of the model patients are randomised to be invited for a Lung Health Check. This is based on the uptake rates set within the model assumptions.

#### Summary

<br/>

#### Distribution of Uptake Population
The chart below is a histogram showing the distribution of the number of patients invited across each of the `r trials` model runs.

```{r y5_uptake_hist, out.width='100%'}

y5_uptake_hist

```

<br/>

### Population uptake
Placeholder.

### Lung Health Checks
Placeholder.

### CT Scans
Placeholder.

### Initial Treatments
Placeholder.

### 3M Treatments
Placeholder.

### 12M Treatments
Placeholder.

### 24M Treatments
Placeholder.


## Key Findings {.tabset .tabset-fade}
***

Placeholder.