---
title: "Lung Health Checks, 5-Year Model"
author: "NHS Transformation Unit"
date: "`r Sys.Date()`"
output: 
html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    toc_collapsed: true
    css: ../config/nhs_tu_theme.css
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

source("../model/lhc_model.R")

```

```{r logo, echo = FALSE}

htmltools::img(src = knitr::image_uri(paste0(here(), "/images/TU_logo_large.png")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:5%; padding:10px;',
               width = "180px",
               heigth = "180px")

```

## Introduction
***

This repository holds the codebase for modelling the demand and capacity requirements for Lung Health Check screening. There is an ambition for all eligible patients aged 55 - 74 years old with a history of smoking to be offered a lung health check by 2029, more information is available [here](https://www.nhs.uk/conditions/lung-health-checks/).


## Year 1 {.tabset .tabset-fade}
***

Placeholder.


### Population uptake
Placeholder.

### Lung Health Checks
Placeholder.

### CT Scans
Placeholder.

### Initial Treatments
Placeholder.

### 3M Treatments
Placeholder.

### 12M Treatments
Placeholder.

### 24M Treatments
Placeholder.


## Year 2 {.tabset .tabset-fade}
***

Placeholder.


### Population uptake
Placeholder.

### Lung Health Checks
Placeholder.

### CT Scans
Placeholder.

### Initial Treatments
Placeholder.

### 3M Treatments
Placeholder.

### 12M Treatments
Placeholder.

### 24M Treatments
Placeholder.


## Year 3 {.tabset .tabset-fade}
***

Placeholder.


### Population uptake
Placeholder.

### Lung Health Checks
Placeholder.

### CT Scans
Placeholder.

### Initial Treatments
Placeholder.

### 3M Treatments
Placeholder.

### 12M Treatments
Placeholder.

### 24M Treatments
Placeholder.


## Year 4 {.tabset .tabset-fade}
***

Placeholder.


### Population uptake
Placeholder.

### Lung Health Checks
Placeholder.

### CT Scans
Placeholder.

### Initial Treatments
Placeholder.

### 3M Treatments
Placeholder.

### 12M Treatments
Placeholder.

### 24M Treatments
Placeholder.


## Year 5 {.tabset .tabset-fade}
***

Placeholder.


### Population uptake
Placeholder.

### Lung Health Checks
Placeholder.

### CT Scans
Placeholder.

### Initial Treatments
Placeholder.

### 3M Treatments
Placeholder.

### 12M Treatments
Placeholder.

### 24M Treatments
Placeholder.