---
title: "Lung Health Checks, 5-Year Model"
author: "NHS Transformation Unit"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    toc_collapsed: true
    css: ../config/nhs_tu_theme.css
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

source("../model/lhc_model.R")
source("../visualisation/visualisations_run.R")

```

```{r logo, echo = FALSE}

htmltools::img(src = knitr::image_uri(paste0(here(), "/images/TU_logo_large.png")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:5%; padding:10px;',
               width = "180px",
               heigth = "180px")

```

## Introduction {.tabset .tabset-fade}
***

### Background to the Model


<br/>

### Assumptions

<br/>


### Pathway

<br/>

## Year 1 Projections {.tabset .tabset-fade}
***

This section provides an overview of the projected activity and outcomes at each point of the pathway during the first year of the model. Within each tab there is a summary of the activity projected from the `r trials` model runs undertaken.


### Population uptake {.tabset .tabset-fade}
In the first stage of the model patients are randomised to be invited for a Lung Health Check. This is based on the uptake rates set within the model assumptions.

#### Summary

<br/>

#### Distribution of Uptake Population
The chart below is a histogram showing the distribution of the number of patients invited across each of the `r trials` model runs.

```{r y1_uptake_hist, out.width='100%'}

y1_uptake_hist

```

<br/>

### Lung Health Checks {.tabset .tabset-fade}
At the next stage patients will be invited to attend a Lung Health Check. Patient's may opt-out of the invite, DNA the appointment or attend for the check. This section provides an overview of the:

* The number of Lung Health Checks performed across each of the model runs.
* The split of the checks undertaken between positive and negative checks.
* The number of negative lung health check patients who will be re-invited in two years.
* The number of patients who declined the appointment and opted-out.

#### LHC Activity
The table below shows a summary of the activity required across the `r trials` model runs:

```{r y1_lhc_activity_table}

```


<br/>

The distribution of LHC appointment activity across these model runs is shown in the histogram below:

```{r y1_lhc_activity_hist, out.width='100%'}

y1_lhc_activity_hist

```

<br/>

#### LHC Outcomes
The table below shows a summary of the split of the number of patients with a positive lung health check and those with a negative result:

```{r y1_lhc_outcome_table}

```

<br/>

The histogram below shows the distribution of these outcomes across the `r trials` model runs:

```{r y1_lhc_outcome_hist, out.width='100%'}

y1_lhc_outcomes_hist

```

<br/>

#### LHC Opt-Outs
The table below shows a summary of the number of patients who opted-out of the invite for a Lung Health Check:

```{r y1_lhc_opt-out_table, out.width='100%'}



```

<br/>

The histogram below shows the distribution of these opt-out numbers across the `r trials` model runs:

```{r y1_lhc_opt-out_hist, out.width='100%'}

y1_lhc_opt_out_hist

```

<br/>

#### LHC Negative Re-invites
The table below shows a summary of the number of patients who had a negative Lung Health Check but need to be re-invited in two years:

```{r y1_lhc_neg_ri_table, out.width='100%'}



```

<br/>

The histogram below shows the distribution of these negative re-invite numbers across the `r trials` model runs:

```{r y1_lhc_neg_ri_hist, out.width='100%'}

y1_lhc_neg_ri_hist

```

<br/>

### CT Scans {.tabset .tabset-fade}
Patients with a positive Lung Health Check will then be referred for a CT scan. Some patients may be excluded from a CT scan, they may require further investigations or their scan may be negative. The probabilities of each of these outcomes are determined from the input assumptions into the model. This section provides an overview of:

* The number of CT scans undertaken
* The breakdown of patients in each outcome following the CT scan
* The number of patients with a negative scan requiring a 24-month follow-up
* The number of patients who DNA scans and opted-out, these patients will be re-invited in later years.

<br/>

#### CT Scan Activity
The table below shows a summary of the activity required across the `r trials` model runs:

```{r y1_ct_activity_table}

```


<br/>

The distribution of CT scan activity across these model runs is shown in the histogram below:

```{r y1_ct_activity_hist, out.width='100%'}

y1_ct_activity_hist

```

<br/>

#### CT Scan Outcomes
The table below shows a summary of the CT scan outcomes across the `r trials` model runs:

```{r y1_ct_outcomes_table}

```


<br/>

The distribution of CT scan outcomes across these model runs is shown in the histogram below:

```{r y1_ct_outcomes_hist, out.width='100%'}

y1_ct_outcomes_hist

```

<br/>

#### Negative Scans Requiring Follow-Up
The table below shows a summary of the number of patients requiring a follow-up across the `r trials` model runs:

```{r y1_ct_neg_fu_table}

```


<br/>

The distribution of 24-month follow-up scans across these model runs is shown in the histogram below:

```{r y1_ct_neg_fu_hist, out.width='100%'}

y1_ct_neg_ri_hist

```

<br/>

#### CT Scan Opt-Outs
The table below shows a summary of the number of patients who DNA their scan and need to be re-invited in the future across the `r trials` model runs:

```{r y1_ct_opt_out_table}

```


<br/>

The distribution of opt-outs across these model runs is shown in the histogram below:

```{r y1_ct_opt_out_hist, out.width='100%'}

y1_ct_opt_out_hist

```

<br/>

### Initial Treatments {.tabset .tabset-fade}
For patients who have a concerning CT scan they will fall within one of three groups. Those requiring further diagnostics, those with an incidental finding and those who will be referred for a three month follow-up scan. For those patients who undergo further diagnostics these will confirm if there is a malignancy requiring treatment. These patients will receive one of eight potential treatment modalities. This is based on the probabilities applied to the model. This section provides an overview of:

* A breakdown of the number of patients who require further diagnostics, have an incidental finding or are placed onto a three month follow-up.
* A breakdown of the diagnostic modality activity for those patients requiring further investigation.
* A breakdown of this group of patients between those with a malignancy and the non-cancer patients.
* A breakdown of the treatment modality activity for the patients with a malignancy.

<br/>

#### Positive Scan Outcomes
The table below shows a summary of the number of patients with a positive CT scan split by outcome across the `r trials` model runs:

```{r y1_init_treat_ct_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y1_init_treat_ct_hist, out.width='100%'}

y1_init_treat_pos_outcomes_hist

```

<br/>

#### Diagnostic Activity
The table below shows a summary of the diagnostic activity by modality for those patients requiring further diagnostics across the `r trials` model runs:

```{r y1_init_treat_diag_table}


```

The distribution of the modality activity across these model runs is shown in the histogram below:

```{r y1_init_treat_diag_hist, out.width='100%'}

y1_init_treat_diags_hist

```

<br/>

#### Confirmed Malignancy
The table below shows a summary of the patients who undergo the additional diagnostics by whether they have a confirmed malignancy or not:

```{r y1_init_treat_malig_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y1_init_treat_malig_hist, out.width='100%'}

y1_init_treat_malig_hist

```

<br/>

#### Treatment Modalities
The table below shows a summary of the treatment modality activity across the `r trials` model runs:

```{r y1_init_treat_mod_table}


```

<br/>

The distribution of the activity across these model runs is shown in the histogram below:

```{r y1_init_treat_mod_hist, out.width='100%'}

y1_init_treat_mods_hist

```

<br/>

### 3 Month Follow-Up Treatments {.tabset .tabset-fade}
At this point in the model the outcomes of those patients on a three month follow-up are determined. At this stage the patients will attend a further CT scan, they may then require additional diagnostics, a malignant diagnosis may be confirmed and treatment provided. This section provides an overview of:

* The number of patients attending the three month follow-up CT Scan
* The outcomes of this scan
* The additional diagnostic activity for each modality for those patients requiring further investigations
* A breakdown of those patients with a confirmed malignancy or not
* A breakdown of the treatment modality activity for those with a confirmed malignancy.

#### CT Scan Activity
The table below shows a summary of the CT scan activity for patients on the three month follow-up across the `r trials` model runs:

```{r y1_m3_treat_ct_activity_table}


```

<br/>

The distribution of this CT scan activity across the model runs is shown in the histogram below:

```{r y1_m3_treat_ct_activity_hist, out.width='100%'}

y1_m3_treat_ct_act_hist

```

<br/>

#### Positive Scan Outcomes
The table below shows a summary of the number of patients with a positive CT scan split by outcome across the `r trials` model runs:

```{r y1_m3_treat_ct_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y1_m3_treat_ct_hist, out.width='100%'}

y1_m3_treat_pos_outcomes_hist

```

<br/>

#### Diagnostic Activity
The table below shows a summary of the diagnostic activity by modality for those patients requiring further diagnostics across the `r trials` model runs:

```{r y1_m3_treat_diag_table}


```

The distribution of the modality activity across these model runs is shown in the histogram below:

```{r y1_m3_treat_diag_hist, out.width='100%'}

y1_init_treat_diags_hist

```

<br/>

#### Confirmed Malignancy
The table below shows a summary of the patients who undergo the additional diagnostics by whether they have a confirmed malignancy or not:

```{r y1_m3_treat_malig_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y1_m3_treat_malig_hist, out.width='100%'}

y1_m3_treat_malig_hist

```

<br/>

#### Treatment Modalities
The table below shows a summary of the treatment modality activity across the `r trials` model runs:

```{r y1_m3_treat_mod_table}


```

<br/>

The distribution of the activity across these model runs is shown in the histogram below:

```{r y1_m3_treat_mod_hist, out.width='100%'}

y1_m3_treat_mods_hist

```

<br/>

### 12 Month Follow-Up Treatments {.tabset .tabset-fade}
At this point in the model the outcomes of those patients on the 12 month follow-up are determined. At this stage the patients will attend a further CT scan, they may then require additional diagnostics, a malignant diagnosis may be confirmed and treatment provided. This section provides an overview of:

* The number of patients attending the 12 month follow-up CT Scan
* The outcomes of this scan
* The additional diagnostic activity for each modality for those patients requiring further investigations
* A breakdown of those patients with a confirmed malignancy or not
* A breakdown of the treatment modality activity for those with a confirmed malignancy.

<br/>

### 24 Month Follow-Up Treatments {.tabset .tabset-fade}
In this final stage of the model the outcomes of those patients on the 24 month follow-up are determined. At this stage the patients will attend a further CT scan, they may then require additional diagnostics, a malignant diagnosis may be confirmed and treatment provided. This section provides an overview of:

* The number of patients attending the three month follow-up CT Scan
* The outcomes of this scan
* The additional diagnostic activity for each modality for those patients requiring further investigations
* A breakdown of those patients with a confirmed malignancy or not
* A breakdown of the treatment modality activity for those with a confirmed malignancy.

<br/>


## Year 2 Projections {.tabset .tabset-fade}
***

This section provides an overview of the projected activity and outcomes at each point of the pathway during the second year of the model. Within each tab there is a summary of the activity projected from the `r trials` model runs undertaken.


### Population uptake {.tabset .tabset-fade}
In the first stage of the model patients are randomised to be invited for a Lung Health Check. This is based on the uptake rates set within the model assumptions.

#### Summary

<br/>

#### Distribution of Uptake Population
The chart below is a histogram showing the distribution of the number of patients invited across each of the `r trials` model runs.

```{r y2_uptake_hist, out.width='100%'}

y2_uptake_hist

```

<br/>


### Lung Health Checks {.tabset .tabset-fade}
At the next stage patients will be invited to attend a Lung Health Check. Patient's may opt-out of the invite, DNA the appointment or attend for the check. This section provides an overview of the:

* The number of Lung Health Checks performed across each of the model runs.
* The split of the checks undertaken between positive and negative checks.
* The number of negative lung health check patients who will be re-invited in two years.
* The number of patients who declined the appointment and opted-out.

#### LHC Activity
The table below shows a summary of the activity required across the `r trials` model runs:

```{r y2_lhc_activity_table}

```


<br/>

The distribution of LHC appointment activity across these model runs is shown in the histogram below:

```{r y2_lhc_activity_hist, out.width='100%'}

y2_lhc_activity_hist

```

<br/>

#### LHC Outcomes
The table below shows a summary of the split of the number of patients with a positive lung health check and those with a negative result:

```{r y2_lhc_outcome_table}

```

<br/>

The histogram below shows the distribution of these outcomes across the `r trials` model runs:

```{r y2_lhc_outcome_hist, out.width='100%'}

y2_lhc_outcomes_hist

```

<br/>

#### LHC Opt-Outs
The table below shows a summary of the number of patients who opted-out of the invite for a Lung Health Check:

```{r y2_lhc_opt-out_table, out.width='100%'}



```

<br/>

The histogram below shows the distribution of these opt-out numbers across the `r trials` model runs:

```{r y2_lhc_opt-out_hist, out.width='100%'}

y2_lhc_opt_out_hist

```

<br/>

#### LHC Negative Re-invites
The table below shows a summary of the number of patients who had a negative Lung Health Check but need to be re-invited in two years:

```{r y2_lhc_neg_ri_table, out.width='100%'}



```

<br/>

The histogram below shows the distribution of these negative re-invite numbers across the `r trials` model runs:

```{r y2_lhc_neg_ri_hist, out.width='100%'}

y2_lhc_neg_ri_hist

```

<br/>

### CT Scans {.tabset .tabset-fade}
Patients with a positive Lung Health Check will then be referred for a CT scan. Some patients may be excluded from a CT scan, they may require further investigations or their scan may be negative. The probabilities of each of these outcomes are determined from the input assumptions into the model. This section provides an overview of:

* The number of CT scans undertaken
* The breakdown of patients in each outcome following the CT scan
* The number of patients with a negative scan requiring a 24-month follow-up
* The number of patients who DNA scans and opted-out, these patients will be re-invited in later years.

<br/>

#### CT Scan Activity
The table below shows a summary of the activity required across the `r trials` model runs:

```{r y2_ct_activity_table}

```


<br/>

The distribution of CT scan activity across these model runs is shown in the histogram below:

```{r y2_ct_activity_hist, out.width='100%'}

y2_ct_activity_hist

```

<br/>

#### CT Scan Outcomes
The table below shows a summary of the CT scan outcomes across the `r trials` model runs:

```{r y2_ct_outcomes_table}

```


<br/>

The distribution of CT scan outcomes across these model runs is shown in the histogram below:

```{r y2_ct_outcomes_hist, out.width='100%'}

y2_ct_outcomes_hist

```

<br/>

#### Negative Scans Requiring Follow-Up
The table below shows a summary of the number of patients requiring a follow-up across the `r trials` model runs:

```{r y2_ct_neg_fu_table}

```


<br/>

The distribution of 24-month follow-up scans across these model runs is shown in the histogram below:

```{r y2_ct_neg_fu_hist, out.width='100%'}

y2_ct_neg_ri_hist

```

<br/>

#### CT Scan Opt-Outs
The table below shows a summary of the number of patients who DNA their scan and need to be re-invited in the future across the `r trials` model runs:

```{r y2_ct_opt_out_table}

```


<br/>

The distribution of opt-outs across these model runs is shown in the histogram below:

```{r y2_ct_opt_out_hist, out.width='100%'}

y2_ct_opt_out_hist

```

<br/>

### Initial Treatments {.tabset .tabset-fade}
For patients who have a concerning CT scan they will fall within one of three groups. Those requiring further diagnostics, those with an incidental finding and those who will be referred for a three month follow-up scan. For those patients who undergo further diagnostics these will confirm if there is a malignancy requiring treatment. These patients will receive one of eight potential treatment modalities. This is based on the probabilities applied to the model. This section provides an overview of:

* A breakdown of the number of patients who require further diagnostics, have an incidental finding or are placed onto a three month follow-up.
* A breakdown of the diagnostic modality activity for those patients requiring further investigation.
* A breakdown of this group of patients between those with a malignancy and the non-cancer patients.
* A breakdown of the treatment modality activity for the patients with a malignancy.

<br/>

#### Positive Scan Outcomes
The table below shows a summary of the number of patients with a positive CT scan split by outcome across the `r trials` model runs:

```{r y2_init_treat_ct_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y2_init_treat_ct_hist, out.width='100%'}

y2_init_treat_pos_outcomes_hist

```

<br/>

#### Diagnostic Activity
The table below shows a summary of the diagnostic activity by modality for those patients requiring further diagnostics across the `r trials` model runs:

```{r y2_init_treat_diag_table}


```

The distribution of the modality activity across these model runs is shown in the histogram below:

```{r y2_init_treat_diag_hist, out.width='100%'}

y2_init_treat_diags_hist

```

<br/>

#### Confirmed Malignancy
The table below shows a summary of the patients who undergo the additional diagnostics by whether they have a confirmed malignancy or not:

```{r y2_init_treat_malig_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y2_init_treat_malig_hist, out.width='100%'}

y2_init_treat_malig_hist

```

<br/>

#### Treatment Modalities
The table below shows a summary of the treatment modality activity across the `r trials` model runs:

```{r y2_init_treat_mod_table}


```

<br/>

The distribution of the activity across these model runs is shown in the histogram below:

```{r y2_init_treat_mod_hist, out.width='100%'}

y2_init_treat_mods_hist

```

<br/>

### 3 Month Follow-Up Treatments {.tabset .tabset-fade}
At this point in the model the outcomes of those patients on a three month follow-up are determined. At this stage the patients will attend a further CT scan, they may then require additional diagnostics, a malignant diagnosis may be confirmed and treatment provided. This section provides an overview of:

* The number of patients attending the three month follow-up CT Scan
* The outcomes of this scan
* The additional diagnostic activity for each modality for those patients requiring further investigations
* A breakdown of those patients with a confirmed malignancy or not
* A breakdown of the treatment modality activity for those with a confirmed malignancy.

#### CT Scan Activity
The table below shows a summary of the CT scan activity for patients on the three month follow-up across the `r trials` model runs:

```{r y2_m3_treat_ct_activity_table}


```

<br/>

The distribution of this CT scan activity across the model runs is shown in the histogram below:

```{r y2_m3_treat_ct_activity_hist, out.width='100%'}

y2_m3_treat_ct_act_hist

```

<br/>

#### Positive Scan Outcomes
The table below shows a summary of the number of patients with a positive CT scan split by outcome across the `r trials` model runs:

```{r y2_m3_treat_ct_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y2_m3_treat_ct_hist, out.width='100%'}

y2_m3_treat_pos_outcomes_hist

```

<br/>

#### Diagnostic Activity
The table below shows a summary of the diagnostic activity by modality for those patients requiring further diagnostics across the `r trials` model runs:

```{r y2_m3_treat_diag_table}


```

The distribution of the modality activity across these model runs is shown in the histogram below:

```{r y2_m3_treat_diag_hist, out.width='100%'}

y2_init_treat_diags_hist

```

<br/>

#### Confirmed Malignancy
The table below shows a summary of the patients who undergo the additional diagnostics by whether they have a confirmed malignancy or not:

```{r y2_m3_treat_malig_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y2_m3_treat_malig_hist, out.width='100%'}

y2_m3_treat_malig_hist

```

<br/>

#### Treatment Modalities
The table below shows a summary of the treatment modality activity across the `r trials` model runs:

```{r y2_m3_treat_mod_table}


```

<br/>

The distribution of the activity across these model runs is shown in the histogram below:

```{r y2_m3_treat_mod_hist, out.width='100%'}

y2_m3_treat_mods_hist

```

<br/>

### 12M Treatments
Placeholder.

### 24M Treatments
Placeholder.


## Year 3 Projections {.tabset .tabset-fade}
***

This section provides an overview of the projected activity and outcomes at each point of the pathway during the third year of the model. Within each tab there is a summary of the activity projected from the `r trials` model runs undertaken.


### Population uptake {.tabset .tabset-fade}
In the first stage of the model patients are randomised to be invited for a Lung Health Check. This is based on the uptake rates set within the model assumptions.

#### Summary

<br/>

#### Distribution of Uptake Population
The chart below is a histogram showing the distribution of the number of patients invited across each of the `r trials` model runs.

```{r y3_uptake_hist, out.width='100%'}

y3_uptake_hist

```

<br/>


### Lung Health Checks {.tabset .tabset-fade}
At the next stage patients will be invited to attend a Lung Health Check. Patient's may opt-out of the invite, DNA the appointment or attend for the check. This section provides an overview of the:

* The number of Lung Health Checks performed across each of the model runs.
* The split of the checks undertaken between positive and negative checks.
* The number of negative lung health check patients who will be re-invited in two years.
* The number of patients who declined the appointment and opted-out.

#### LHC Activity
The table below shows a summary of the activity required across the `r trials` model runs:

```{r y3_lhc_activity_table}

```


<br/>

The distribution of LHC appointment activity across these model runs is shown in the histogram below:

```{r y3_lhc_activity_hist, out.width='100%'}

y3_lhc_activity_hist

```

<br/>

#### LHC Outcomes
The table below shows a summary of the split of the number of patients with a positive lung health check and those with a negative result:

```{r y3_lhc_outcome_table}

```

<br/>

The histogram below shows the distribution of these outcomes across the `r trials` model runs:

```{r y3_lhc_outcome_hist, out.width='100%'}

y3_lhc_outcomes_hist

```

<br/>

#### LHC Opt-Outs
The table below shows a summary of the number of patients who opted-out of the invite for a Lung Health Check:

```{r y3_lhc_opt-out_table, out.width='100%'}



```

<br/>

The histogram below shows the distribution of these opt-out numbers across the `r trials` model runs:

```{r y3_lhc_opt-out_hist, out.width='100%'}

y3_lhc_opt_out_hist

```

<br/>

#### LHC Negative Re-invites
The table below shows a summary of the number of patients who had a negative Lung Health Check but need to be re-invited in two years:

```{r y3_lhc_neg_ri_table, out.width='100%'}



```

<br/>

The histogram below shows the distribution of these negative re-invite numbers across the `r trials` model runs:

```{r y3_lhc_neg_ri_hist, out.width='100%'}

y3_lhc_neg_ri_hist

```

<br/>

### CT Scans {.tabset .tabset-fade}
Patients with a positive Lung Health Check will then be referred for a CT scan. Some patients may be excluded from a CT scan, they may require further investigations or their scan may be negative. The probabilities of each of these outcomes are determined from the input assumptions into the model. This section provides an overview of:

* The number of CT scans undertaken
* The breakdown of patients in each outcome following the CT scan
* The number of patients with a negative scan requiring a 24-month follow-up
* The number of patients who DNA scans and opted-out, these patients will be re-invited in later years.

<br/>

#### CT Scan Activity
The table below shows a summary of the activity required across the `r trials` model runs:

```{r y3_ct_activity_table}

```


<br/>

The distribution of CT scan activity across these model runs is shown in the histogram below:

```{r y3_ct_activity_hist, out.width='100%'}

y3_ct_activity_hist

```

<br/>

#### CT Scan Outcomes
The table below shows a summary of the CT scan outcomes across the `r trials` model runs:

```{r y3_ct_outcomes_table}

```


<br/>

The distribution of CT scan outcomes across these model runs is shown in the histogram below:

```{r y3_ct_outcomes_hist, out.width='100%'}

y3_ct_outcomes_hist

```

<br/>

#### Negative Scans Requiring Follow-Up
The table below shows a summary of the number of patients requiring a follow-up across the `r trials` model runs:

```{r y3_ct_neg_fu_table}

```


<br/>

The distribution of 24-month follow-up scans across these model runs is shown in the histogram below:

```{r y3_ct_neg_fu_hist, out.width='100%'}

y3_ct_neg_ri_hist

```

<br/>

#### CT Scan Opt-Outs
The table below shows a summary of the number of patients who DNA their scan and need to be re-invited in the future across the `r trials` model runs:

```{r y3_ct_opt_out_table}

```


<br/>

The distribution of opt-outs across these model runs is shown in the histogram below:

```{r y3_ct_opt_out_hist, out.width='100%'}

y3_ct_opt_out_hist

```

<br/>

### Initial Treatments {.tabset .tabset-fade}
For patients who have a concerning CT scan they will fall within one of three groups. Those requiring further diagnostics, those with an incidental finding and those who will be referred for a three month follow-up scan. For those patients who undergo further diagnostics these will confirm if there is a malignancy requiring treatment. These patients will receive one of eight potential treatment modalities. This is based on the probabilities applied to the model. This section provides an overview of:

* A breakdown of the number of patients who require further diagnostics, have an incidental finding or are placed onto a three month follow-up.
* A breakdown of the diagnostic modality activity for those patients requiring further investigation.
* A breakdown of this group of patients between those with a malignancy and the non-cancer patients.
* A breakdown of the treatment modality activity for the patients with a malignancy.

<br/>

#### Positive Scan Outcomes
The table below shows a summary of the number of patients with a positive CT scan split by outcome across the `r trials` model runs:

```{r y3_init_treat_ct_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y3_init_treat_ct_hist, out.width='100%'}

y3_init_treat_pos_outcomes_hist

```

<br/>

#### Diagnostic Activity
The table below shows a summary of the diagnostic activity by modality for those patients requiring further diagnostics across the `r trials` model runs:

```{r y3_init_treat_diag_table}


```

The distribution of the modality activity across these model runs is shown in the histogram below:

```{r y3_init_treat_diag_hist, out.width='100%'}

y3_init_treat_diags_hist

```

<br/>

#### Confirmed Malignancy
The table below shows a summary of the patients who undergo the additional diagnostics by whether they have a confirmed malignancy or not:

```{r y3_init_treat_malig_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y3_init_treat_malig_hist, out.width='100%'}

y3_init_treat_malig_hist

```

<br/>

#### Treatment Modalities
The table below shows a summary of the treatment modality activity across the `r trials` model runs:

```{r y3_init_treat_mod_table}


```

<br/>

The distribution of the activity across these model runs is shown in the histogram below:

```{r y3_init_treat_mod_hist, out.width='100%'}

y3_init_treat_mods_hist

```

<br/>

### 3 Month Follow-Up Treatments {.tabset .tabset-fade}
At this point in the model the outcomes of those patients on a three month follow-up are determined. At this stage the patients will attend a further CT scan, they may then require additional diagnostics, a malignant diagnosis may be confirmed and treatment provided. This section provides an overview of:

* The number of patients attending the three month follow-up CT Scan
* The outcomes of this scan
* The additional diagnostic activity for each modality for those patients requiring further investigations
* A breakdown of those patients with a confirmed malignancy or not
* A breakdown of the treatment modality activity for those with a confirmed malignancy.

#### CT Scan Activity
The table below shows a summary of the CT scan activity for patients on the three month follow-up across the `r trials` model runs:

```{r y3_m3_treat_ct_activity_table}


```

<br/>

The distribution of this CT scan activity across the model runs is shown in the histogram below:

```{r y3_m3_treat_ct_activity_hist, out.width='100%'}

y3_m3_treat_ct_act_hist

```

<br/>

#### Positive Scan Outcomes
The table below shows a summary of the number of patients with a positive CT scan split by outcome across the `r trials` model runs:

```{r y3_m3_treat_ct_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y3_m3_treat_ct_hist, out.width='100%'}

y3_m3_treat_pos_outcomes_hist

```

<br/>

#### Diagnostic Activity
The table below shows a summary of the diagnostic activity by modality for those patients requiring further diagnostics across the `r trials` model runs:

```{r y3_m3_treat_diag_table}


```

The distribution of the modality activity across these model runs is shown in the histogram below:

```{r y3_m3_treat_diag_hist, out.width='100%'}

y3_init_treat_diags_hist

```

<br/>

#### Confirmed Malignancy
The table below shows a summary of the patients who undergo the additional diagnostics by whether they have a confirmed malignancy or not:

```{r y3_m3_treat_malig_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y3_m3_treat_malig_hist, out.width='100%'}

y3_m3_treat_malig_hist

```

<br/>

#### Treatment Modalities
The table below shows a summary of the treatment modality activity across the `r trials` model runs:

```{r y3_m3_treat_mod_table}


```

<br/>

The distribution of the activity across these model runs is shown in the histogram below:

```{r y3_m3_treat_mod_hist, out.width='100%'}

y3_m3_treat_mods_hist

```

<br/>


### 12M Treatments
Placeholder.

### 24M Treatments
Placeholder.


## Year 4 Projections {.tabset .tabset-fade}
***

This section provides an overview of the projected activity and outcomes at each point of the pathway during the fourth year of the model. Within each tab there is a summary of the activity projected from the `r trials` model runs undertaken.


### Population uptake {.tabset .tabset-fade}
In the first stage of the model patients are randomised to be invited for a Lung Health Check. This is based on the uptake rates set within the model assumptions.

#### Summary

<br/>

#### Distribution of Uptake Population
The chart below is a histogram showing the distribution of the number of patients invited across each of the `r trials` model runs.

```{r y4_uptake_hist, out.width='100%'}

y4_uptake_hist

```

<br/>

### Lung Health Checks {.tabset .tabset-fade}
At the next stage patients will be invited to attend a Lung Health Check. Patient's may opt-out of the invite, DNA the appointment or attend for the check. This section provides an overview of the:

* The number of Lung Health Checks performed across each of the model runs.
* The split of the checks undertaken between positive and negative checks.
* The number of negative lung health check patients who will be re-invited in two years.
* The number of patients who declined the appointment and opted-out.

#### LHC Activity
The table below shows a summary of the activity required across the `r trials` model runs:

```{r y4_lhc_activity_table}

```


<br/>

The distribution of LHC appointment activity across these model runs is shown in the histogram below:

```{r y4_lhc_activity_hist, out.width='100%'}

y4_lhc_activity_hist

```

<br/>

#### LHC Outcomes
The table below shows a summary of the split of the number of patients with a positive lung health check and those with a negative result:

```{r y4_lhc_outcome_table}

```

<br/>

The histogram below shows the distribution of these outcomes across the `r trials` model runs:

```{r y4_lhc_outcome_hist, out.width='100%'}

y4_lhc_outcomes_hist

```

<br/>

#### LHC Opt-Outs
The table below shows a summary of the number of patients who opted-out of the invite for a Lung Health Check:

```{r y4_lhc_opt-out_table, out.width='100%'}



```

<br/>

The histogram below shows the distribution of these opt-out numbers across the `r trials` model runs:

```{r y4_lhc_opt-out_hist, out.width='100%'}

y4_lhc_opt_out_hist

```

<br/>

#### LHC Negative Re-invites
The table below shows a summary of the number of patients who had a negative Lung Health Check but need to be re-invited in two years:

```{r y4_lhc_neg_ri_table, out.width='100%'}



```

<br/>

The histogram below shows the distribution of these negative re-invite numbers across the `r trials` model runs:

```{r y4_lhc_neg_ri_hist, out.width='100%'}

y4_lhc_neg_ri_hist

```

<br/>

### CT Scans {.tabset .tabset-fade}
Patients with a positive Lung Health Check will then be referred for a CT scan. Some patients may be excluded from a CT scan, they may require further investigations or their scan may be negative. The probabilities of each of these outcomes are determined from the input assumptions into the model. This section provides an overview of:

* The number of CT scans undertaken
* The breakdown of patients in each outcome following the CT scan
* The number of patients with a negative scan requiring a 24-month follow-up
* The number of patients who DNA scans and opted-out, these patients will be re-invited in later years.

<br/>

#### CT Scan Activity
The table below shows a summary of the activity required across the `r trials` model runs:

```{r y4_ct_activity_table}

```


<br/>

The distribution of CT scan activity across these model runs is shown in the histogram below:

```{r y4_ct_activity_hist, out.width='100%'}

y4_ct_activity_hist

```

<br/>

#### CT Scan Outcomes
The table below shows a summary of the CT scan outcomes across the `r trials` model runs:

```{r y4_ct_outcomes_table}

```


<br/>

The distribution of CT scan outcomes across these model runs is shown in the histogram below:

```{r y4_ct_outcomes_hist, out.width='100%'}

y4_ct_outcomes_hist

```

<br/>

#### Negative Scans Requiring Follow-Up
The table below shows a summary of the number of patients requiring a follow-up across the `r trials` model runs:

```{r y4_ct_neg_fu_table}

```


<br/>

The distribution of 24-month follow-up scans across these model runs is shown in the histogram below:

```{r y4_ct_neg_fu_hist, out.width='100%'}

y4_ct_neg_ri_hist

```

<br/>

#### CT Scan Opt-Outs
The table below shows a summary of the number of patients who DNA their scan and need to be re-invited in the future across the `r trials` model runs:

```{r y4_ct_opt_out_table}

```


<br/>

The distribution of opt-outs across these model runs is shown in the histogram below:

```{r y4_ct_opt_out_hist, out.width='100%'}

y4_ct_opt_out_hist

```

<br/>

### Initial Treatments {.tabset .tabset-fade}
For patients who have a concerning CT scan they will fall within one of three groups. Those requiring further diagnostics, those with an incidental finding and those who will be referred for a three month follow-up scan. For those patients who undergo further diagnostics these will confirm if there is a malignancy requiring treatment. These patients will receive one of eight potential treatment modalities. This is based on the probabilities applied to the model. This section provides an overview of:

* A breakdown of the number of patients who require further diagnostics, have an incidental finding or are placed onto a three month follow-up.
* A breakdown of the diagnostic modality activity for those patients requiring further investigation.
* A breakdown of this group of patients between those with a malignancy and the non-cancer patients.
* A breakdown of the treatment modality activity for the patients with a malignancy.

<br/>

#### Positive Scan Outcomes
The table below shows a summary of the number of patients with a positive CT scan split by outcome across the `r trials` model runs:

```{r y4_init_treat_ct_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y4_init_treat_ct_hist, out.width='100%'}

y4_init_treat_pos_outcomes_hist

```

<br/>

#### Diagnostic Activity
The table below shows a summary of the diagnostic activity by modality for those patients requiring further diagnostics across the `r trials` model runs:

```{r y4_init_treat_diag_table}


```

The distribution of the modality activity across these model runs is shown in the histogram below:

```{r y4_init_treat_diag_hist, out.width='100%'}

y4_init_treat_diags_hist

```

<br/>

#### Confirmed Malignancy
The table below shows a summary of the patients who undergo the additional diagnostics by whether they have a confirmed malignancy or not:

```{r y4_init_treat_malig_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y4_init_treat_malig_hist, out.width='100%'}

y4_init_treat_malig_hist

```

<br/>

#### Treatment Modalities
The table below shows a summary of the treatment modality activity across the `r trials` model runs:

```{r y4_init_treat_mod_table}


```

<br/>

The distribution of the activity across these model runs is shown in the histogram below:

```{r y4_init_treat_mod_hist, out.width='100%'}

y4_init_treat_mods_hist

```

<br/>

### 3 Month Follow-Up Treatments {.tabset .tabset-fade}
At this point in the model the outcomes of those patients on a three month follow-up are determined. At this stage the patients will attend a further CT scan, they may then require additional diagnostics, a malignant diagnosis may be confirmed and treatment provided. This section provides an overview of:

* The number of patients attending the three month follow-up CT Scan
* The outcomes of this scan
* The additional diagnostic activity for each modality for those patients requiring further investigations
* A breakdown of those patients with a confirmed malignancy or not
* A breakdown of the treatment modality activity for those with a confirmed malignancy.

#### CT Scan Activity
The table below shows a summary of the CT scan activity for patients on the three month follow-up across the `r trials` model runs:

```{r y4_m3_treat_ct_activity_table}


```

<br/>

The distribution of this CT scan activity across the model runs is shown in the histogram below:

```{r y4_m3_treat_ct_activity_hist, out.width='100%'}

y4_m3_treat_ct_act_hist

```

<br/>

#### Positive Scan Outcomes
The table below shows a summary of the number of patients with a positive CT scan split by outcome across the `r trials` model runs:

```{r y4_m3_treat_ct_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y4_m3_treat_ct_hist, out.width='100%'}

y4_m3_treat_pos_outcomes_hist

```

<br/>

#### Diagnostic Activity
The table below shows a summary of the diagnostic activity by modality for those patients requiring further diagnostics across the `r trials` model runs:

```{r y4_m3_treat_diag_table}


```

The distribution of the modality activity across these model runs is shown in the histogram below:

```{r y4_m3_treat_diag_hist, out.width='100%'}

y4_init_treat_diags_hist

```

<br/>

#### Confirmed Malignancy
The table below shows a summary of the patients who undergo the additional diagnostics by whether they have a confirmed malignancy or not:

```{r y4_m3_treat_malig_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y4_m3_treat_malig_hist, out.width='100%'}

y4_m3_treat_malig_hist

```

<br/>

#### Treatment Modalities
The table below shows a summary of the treatment modality activity across the `r trials` model runs:

```{r y4_m3_treat_mod_table}


```

<br/>

The distribution of the activity across these model runs is shown in the histogram below:

```{r y4_m3_treat_mod_hist, out.width='100%'}

y4_m3_treat_mods_hist

```

<br/>

### 12M Treatments
Placeholder.

### 24M Treatments
Placeholder.


## Year 5 Projections {.tabset .tabset-fade}
***

This section provides an overview of the projected activity and outcomes at each point of the pathway during the final year of the model. Within each tab there is a summary of the activity projected from the `r trials` model runs undertaken.


### Population uptake {.tabset .tabset-fade}
In the first stage of the model patients are randomised to be invited for a Lung Health Check. This is based on the uptake rates set within the model assumptions.

#### Summary

<br/>

#### Distribution of Uptake Population
The chart below is a histogram showing the distribution of the number of patients invited across each of the `r trials` model runs.

```{r y5_uptake_hist, out.width='100%'}

y5_uptake_hist

```

<br/>

### Lung Health Checks {.tabset .tabset-fade}
At the next stage patients will be invited to attend a Lung Health Check. Patient's may opt-out of the invite, DNA the appointment or attend for the check. This section provides an overview of the:

* The number of Lung Health Checks performed across each of the model runs.
* The split of the checks undertaken between positive and negative checks.
* The number of negative lung health check patients who will be re-invited in two years.
* The number of patients who declined the appointment and opted-out.

#### LHC Activity
The table below shows a summary of the activity required across the `r trials` model runs:

```{r y5_lhc_activity_table}

```


<br/>

The distribution of LHC appointment activity across these model runs is shown in the histogram below:

```{r y5_lhc_activity_hist, out.width='100%'}

y5_lhc_activity_hist

```

<br/>

#### LHC Outcomes
The table below shows a summary of the split of the number of patients with a positive lung health check and those with a negative result:

```{r y5_lhc_outcome_table}

```

<br/>

The histogram below shows the distribution of these outcomes across the `r trials` model runs:

```{r y5_lhc_outcome_hist, out.width='100%'}

y5_lhc_outcomes_hist

```

<br/>

#### LHC Opt-Outs
The table below shows a summary of the number of patients who opted-out of the invite for a Lung Health Check:

```{r y5_lhc_opt-out_table, out.width='100%'}



```

<br/>

The histogram below shows the distribution of these opt-out numbers across the `r trials` model runs:

```{r y5_lhc_opt-out_hist, out.width='100%'}

y5_lhc_opt_out_hist

```

<br/>

#### LHC Negative Re-invites
The table below shows a summary of the number of patients who had a negative Lung Health Check but need to be re-invited in two years:

```{r y5_lhc_neg_ri_table, out.width='100%'}



```

<br/>

The histogram below shows the distribution of these negative re-invite numbers across the `r trials` model runs:

```{r y5_lhc_neg_ri_hist, out.width='100%'}

y5_lhc_neg_ri_hist

```

<br/>

### CT Scans {.tabset .tabset-fade}
Patients with a positive Lung Health Check will then be referred for a CT scan. Some patients may be excluded from a CT scan, they may require further investigations or their scan may be negative. The probabilities of each of these outcomes are determined from the input assumptions into the model. This section provides an overview of:

* The number of CT scans undertaken
* The breakdown of patients in each outcome following the CT scan
* The number of patients with a negative scan requiring a 24-month follow-up
* The number of patients who DNA scans and opted-out, these patients will be re-invited in later years.

<br/>

#### CT Scan Activity
The table below shows a summary of the activity required across the `r trials` model runs:

```{r y5_ct_activity_table}

```


<br/>

The distribution of CT scan activity across these model runs is shown in the histogram below:

```{r y5_ct_activity_hist, out.width='100%'}

y5_ct_activity_hist

```

<br/>

#### CT Scan Outcomes
The table below shows a summary of the CT scan outcomes across the `r trials` model runs:

```{r y5_ct_outcomes_table}

```


<br/>

The distribution of CT scan outcomes across these model runs is shown in the histogram below:

```{r y5_ct_outcomes_hist, out.width='100%'}

y5_ct_outcomes_hist

```

<br/>

#### Negative Scans Requiring Follow-Up
The table below shows a summary of the number of patients requiring a follow-up across the `r trials` model runs:

```{r y5_ct_neg_fu_table}

```


<br/>

The distribution of 24-month follow-up scans across these model runs is shown in the histogram below:

```{r y5_ct_neg_fu_hist, out.width='100%'}

y5_ct_neg_ri_hist

```

<br/>

#### CT Scan Opt-Outs
The table below shows a summary of the number of patients who DNA their scan and need to be re-invited in the future across the `r trials` model runs:

```{r y5_ct_opt_out_table}

```


<br/>

The distribution of opt-outs across these model runs is shown in the histogram below:

```{r y5_ct_opt_out_hist, out.width='100%'}

y5_ct_opt_out_hist

```

<br/>

### Initial Treatments {.tabset .tabset-fade}
For patients who have a concerning CT scan they will fall within one of three groups. Those requiring further diagnostics, those with an incidental finding and those who will be referred for a three month follow-up scan. For those patients who undergo further diagnostics these will confirm if there is a malignancy requiring treatment. These patients will receive one of eight potential treatment modalities. This is based on the probabilities applied to the model. This section provides an overview of:

* A breakdown of the number of patients who require further diagnostics, have an incidental finding or are placed onto a three month follow-up.
* A breakdown of the diagnostic modality activity for those patients requiring further investigation.
* A breakdown of this group of patients between those with a malignancy and the non-cancer patients.
* A breakdown of the treatment modality activity for the patients with a malignancy.

<br/>

#### Positive Scan Outcomes
The table below shows a summary of the number of patients with a positive CT scan split by outcome across the `r trials` model runs:

```{r y5_init_treat_ct_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y5_init_treat_ct_hist, out.width='100%'}

y5_init_treat_pos_outcomes_hist

```

<br/>

#### Diagnostic Activity
The table below shows a summary of the diagnostic activity by modality for those patients requiring further diagnostics across the `r trials` model runs:

```{r y5_init_treat_diag_table}


```

The distribution of the modality activity across these model runs is shown in the histogram below:

```{r y5_init_treat_diag_hist, out.width='100%'}

y5_init_treat_diags_hist

```

<br/>

#### Confirmed Malignancy
The table below shows a summary of the patients who undergo the additional diagnostics by whether they have a confirmed malignancy or not:

```{r y5_init_treat_malig_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y5_init_treat_malig_hist, out.width='100%'}

y5_init_treat_malig_hist

```

<br/>

#### Treatment Modalities
The table below shows a summary of the treatment modality activity across the `r trials` model runs:

```{r y5_init_treat_mod_table}


```

<br/>

The distribution of the activity across these model runs is shown in the histogram below:

```{r y5_init_treat_mod_hist, out.width='100%'}

y5_init_treat_mods_hist

```

<br/>

### 3 Month Follow-Up Treatments {.tabset .tabset-fade}
At this point in the model the outcomes of those patients on a three month follow-up are determined. At this stage the patients will attend a further CT scan, they may then require additional diagnostics, a malignant diagnosis may be confirmed and treatment provided. This section provides an overview of:

* The number of patients attending the three month follow-up CT Scan
* The outcomes of this scan
* The additional diagnostic activity for each modality for those patients requiring further investigations
* A breakdown of those patients with a confirmed malignancy or not
* A breakdown of the treatment modality activity for those with a confirmed malignancy.

#### CT Scan Activity
The table below shows a summary of the CT scan activity for patients on the three month follow-up across the `r trials` model runs:

```{r y5_m3_treat_ct_activity_table}


```

<br/>

The distribution of this CT scan activity across the model runs is shown in the histogram below:

```{r y5_m3_treat_ct_activity_hist, out.width='100%'}

y5_m3_treat_ct_act_hist

```

<br/>

#### Positive Scan Outcomes
The table below shows a summary of the number of patients with a positive CT scan split by outcome across the `r trials` model runs:

```{r y5_m3_treat_ct_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y5_m3_treat_ct_hist, out.width='100%'}

y5_m3_treat_pos_outcomes_hist

```

<br/>

#### Diagnostic Activity
The table below shows a summary of the diagnostic activity by modality for those patients requiring further diagnostics across the `r trials` model runs:

```{r y5_m3_treat_diag_table}


```

The distribution of the modality activity across these model runs is shown in the histogram below:

```{r y5_m3_treat_diag_hist, out.width='100%'}

y5_init_treat_diags_hist

```

<br/>

#### Confirmed Malignancy
The table below shows a summary of the patients who undergo the additional diagnostics by whether they have a confirmed malignancy or not:

```{r y5_m3_treat_malig_table}


```

<br/>

The distribution of these outcomes across these model runs is shown in the histogram below:

```{r y5_m3_treat_malig_hist, out.width='100%'}

y5_m3_treat_malig_hist

```

<br/>

#### Treatment Modalities
The table below shows a summary of the treatment modality activity across the `r trials` model runs:

```{r y5_m3_treat_mod_table}


```

<br/>

The distribution of the activity across these model runs is shown in the histogram below:

```{r y5_m3_treat_mod_hist, out.width='100%'}

y5_m3_treat_mods_hist

```

<br/>

### 12 Month Follow-Up Treatments {.tabset .tabset-fade}
At this point in the model the outcomes of those patients on the 12 month follow-up are determined. At this stage the patients will attend a further CT scan, they may then require additional diagnostics, a malignant diagnosis may be confirmed and treatment provided. This section provides an overview of:

* The number of patients attending the three month follow-up CT Scan
* The outcomes of this scan
* The additional diagnostic activity for each modality for those patients requiring further investigations
* A breakdown of those patients with a confirmed malignancy or not
* A breakdown of the treatment modality activity for those with a confirmed malignancy.

<br/>

### 24 Month Follow-Up Treatments {.tabset .tabset-fade}
In this final stage of the model the outcomes of those patients on the 24 month follow-up are determined. At this stage the patients will attend a further CT scan, they may then require additional diagnostics, a malignant diagnosis may be confirmed and treatment provided. This section provides an overview of:

* The number of patients attending the three month follow-up CT Scan
* The outcomes of this scan
* The additional diagnostic activity for each modality for those patients requiring further investigations
* A breakdown of those patients with a confirmed malignancy or not
* A breakdown of the treatment modality activity for those with a confirmed malignancy.

<br/>